---
title: "244_Assignment3_COLON"
author: "Mario Colon"
date: "March 2, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Load Packages

```{r}

library(tidyverse)
library(forecast)
library(tseries)
library(sf)
library(tmap)
library(maps)

```


#Task 2: Reading and Short Answer

#Task 3: Truckee River Flows (2000 – 2016)

```{r}

truckee <- read_csv("truckee_flow.csv")

truck_ts <- ts(truckee$mean_va, frequency = 12, start = c(2000,1)) #frequency = 12 means months/year
truck_ts
class(truck_ts)
plot(truck_ts)
d_truckee <- decompose(truck_ts)
plot(d_truckee)

#ARIMA

adf_truckee <- adf.test(truck_ts)
adf_truckee

#based in outcome (p < 0.01) retain the alternative that the data ARE stationary

#Holt-Winters

hw_truckee <- HoltWinters(truck_ts) 
plot(hw_truckee)


forecast_truckee <- forecast(hw_truckee, h = 60) 
plot(forecast_truckee)

hist(forecast_truckee$residuals)

```
Figure 1. [ ]


#Task 4. Mapping California’s National Parks

```{r}

counties <- st_read(dsn = ".", layer = "california_county_shape_file")
nps <- st_read(dsn = ".", layer = "nps_boundary")

CA_nps <- nps %>% 
  select(STATE, UNIT_TYPE) %>% 
  filter(STATE == "CA") %>% 
  filter(UNIT_TYPE == "National Park")


st_crs(counties) <- 4326 #standard reference for map projection (1984)

st_transform(CA_nps, crs = 4326) #transform CA_nps to match counties 


CA_NPS_Buffer <-CA_nps %>%
 st_buffer(.01)

ggplot(CA_nps) +
  geom_sf(data = counties) +
  geom_sf(aes(fill = "National Park"), show.legend = FALSE) +
  geom_sf(data = CA_NPS_Buffer, fill = NA, colour = "green", size = .5) +
  theme_bw() +
  theme(panel.grid.major = element_line(colour = 'transparent'))

ggplot(CA_nps) +
  geom_sf(data = counties) +
  geom_sf(aes(fill = "National Park"), colour = "blue", fill = "darkgreen") +
  theme_bw() +
  theme(panel.grid.major = element_line(colour = 'transparent'))



```

##Task 5. LTER Lizards in the Northern Chihuahuan Desert

```{r}

lizards <- read_csv("lter_lizard_pitfall.csv")
lizards[lizards =="."]<-NA

#(1) For all lizards trapped at site ‘CALI’, do weights of male and female adult lizards differ significantly?


m_cali <- lizards %>% 
  select(site, sex, weight) %>% 
  filter(site == "CALI", sex == "M")

mw <- m_cali$weight

f_cali <- lizards %>% 
  select(site, sex, weight) %>% 
  filter(site == "CALI", sex == "F")

fw <- f_cali$weight

mw <- as.numeric(mw)
fw <- as.numeric(fw)

lizard_t_test <- var.test(mw,fw)
lizard_t_test

t.test(mw, fw, var.equal = TRUE)

   #(2) For lizards trapped at the ‘CALI’ site, is there a significant difference in the proportion of adult male and female lizards with broken tails?


cali_tail <- lizards %>% 
  select(site, sex, tail) %>% 
  filter(site =="CALI") %>%
  filter(tail !=".") %>% 
  filter(sex !="J") %>% 
  filter(sex !=".")

View(cali_tail)

abs_lizard_tail <- table(cali_tail$sex, cali_tail$tail)

abs_lizard_tail

cali_lizard_tail <- matrix( c(18, 10, 59, 46), nrow=2, ncol=2, byrow=FALSE)

rownames(cali_lizard_tail) <- c("F", "M")
colnames(cali_lizard_tail) <- c("B","W")

cali_lizard_tail

prop.test(cali_lizard_tail)


```

(1)

Live-trapping of lizards (sampling-with-replacement) in the Northern Chihuahua Desert near White Sands, NM from 1989 to 1990 found that though mean weight for female lizards (n = 79) was 0.86 grams greater than males (n = 58), the result was not significant (t(130) = -0.7, p = 0.427).

(2)

There is not a significant difference in the proportion of adult male (n = 56) and female (n = 77) lizards with broken tails ($\chi$^2^(1, n = 133) = 0.31, p = 0.579).