---
title: "Lab_3"
output: html_document
auhor: "Mario Colon"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Boostrapping Pengin Flipper Lengths

a. Get packages

```{r load_packages}

library(tidyverse)
library(boot)
library(nlstools)
```

b. Import data and manipulate

```{r import_data}

penguins <- read_csv("~/Downloads/244/Lab_3/penguins.csv")

flip <- penguins %>% 
  filter(sex == "FEMALE") %>% 
  select(flipper_length) 

flip_v <- flip$flipper_length

```

c. Create a function to calculate the means of the bootstrap samples

```{r bootstrap}

mean_fun <- function(x,i) {mean (x[i])}

```

d. Bootstrap flip_v

```{r bootstrap_1}

boot_10000 <- boot(flip_v, mean_fun, R = 10000)
#boot_10000$t
hist(boot_10000$t)



```

e. Find the confidence interval based on the sampling distribution using function boot.ci()

```{r sample_dist}

penguin_ci <- boot.ci(boot_10000, conf = .95, type = "perc")
penguin_ci 


```

##Cell Growth

a. Read Data

```{r cell_data}

CellGrowth <- read_csv("~/Downloads/244/Lab_3/CellGrowth.csv")

```

b. look at it

```{r exploration}

ggplot(CellGrowth, aes(x = Time, y = CellCount)) +
  geom_point()



```

Ct = A / (1 + Be^-rt)

Estimate for K ~ 3700
Estimate for C0 ~ 2000
Estimate for B ~ .85


Create a linear model between the natural log of CellCount and Time for the first 5 observations (these look like they might follow exponential gorwth). The slope of that line is an estimate for the growth rate constant

```{r lm}

r_est <- lm(log(CellGrowth$CellCount[1:5]) ~ CellGrowth$Time[1:5])
r_est
#r starting estimate = 0.1035
```

Estimate for A ~ 3700
Estimate for B ~ .85
Estimate for r ~ 0.1035

NLS for estimating parameter values for logistic growth, starting with our estimate for A, B, and r

C = A / (1 + Be^-rt)

```{r estimates}

cell_fit <- nls(CellCount ~ A / (1 + B*exp(-r*Time)),
                data = CellGrowth,
                start = list(A = 3700, B = 0.85, r = 0.1035),
                trace = TRUE
                )

```

```{r more_fun}

A <- coef(cell_fit)[1]
B <- coef(cell_fit)[2]
r <- coef(cell_fit)[3]
```

Create a time sequence (from 0 to 20 hours, and I want there to be 100). Then I'm going to plug that into my model to find the predicted cell population size

```{r}

time_seq <- seq(0, 20, length = 100)
time_seq
cell_pred <- A/(1+B*exp(-r*time_seq))
cell_pred

pred_df <- data.frame(time_seq, cell_pred)
pred_df

```

Create a graph of original data + predictive model line

```{r}

ggplot(CellGrowth, aes(x=Time, y=CellCount)) +
  geom_point(color = "blue", size = 3) +
  theme_bw() +
  geom_line(data = pred_df, aes(x = time_seq, y = cell_pred))

```

