---
title: "Lab 6 - Time Series Exploration and Forecasting"
author: "Mario Colon"
date: "February 22, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##1. Get Packages

```{r}


library(tidyverse)
library(forecast)
library(tseries)

```

##2. Load Date

```{r}

energy <- read_csv("energy.csv")
class(energy)

```
 
##3. Convert to 'ts' data

```{r}

res_ts <- ts(energy$res_total, frequency = 12, start = c(1973,1)) #frequency = 12 means months/year
#res_ts
class(res_ts) #should be ts data

```

Simple Plot :

```{r}

plot(res_ts)

```

## Decompose the ts data

decompose() function 

```{r}

res_dc <- decompose(res_ts)
plot(res_dc)

```

##5. Other fast, cool ways to explore you ts data

monthplot() - plots subseries from time series 

```{r}

monthplot(res_ts)

```

```{r}

ggseasonplot(res_ts) +
  theme_bw()

```

##6. Simple moving average (smoothing)

Use the'ma' functionin forecast package

```{r}

sma_res <- ma(res_ts, order = 12) #calculates moving average
plot(res_ts)
lines(sma_res, col = "red")

```

##7. Explore autocorrelation (ACT)

Good way to explore seasonality 

1. Basic way (using acf)
2. gg way (using ggtsdisplay)

```{r}
#basic

acf(res_ts)

#gg way

ggtsdisplay(res_ts)

```

##Augmented Dickey - Fuller Test for Stationarity 

Null Hypothesis: data are NOT stationary 
Alternative Hypothesis: data ARE stationary 

If p < 0.05 (assuming a significance level of alpha = 0.05), I would retain the alternative hypothesis that the data ARE stationary 

```{r}

adf_res <- adf.test(res_ts) #based in outcome (p < 0.01, retain the alternative that the data ARE stationary)
adf_res

```

##9. Holt Winters Exponential Smoothing

```{r}

res_hw <- HoltWinters(res_ts) 
plot(res_hw)

res_forecast <- forecast(res_hw, h = 120) #120 means 120 months 
plot(res_forecast)

hist(res_forecast$residuals)

```

##10. ARIMA using auto.arima() function 

```{r}

res_pdq <- auto.arima(res_ts)

res_pdq

```

Nonseasonal/seasonal PDQ: (1,0,2)(0,1,1)

```{r}

res_arima <- arima(res_ts, order = c(1,0,2), seasonal = list(order = c(0,1,1)))

```

Evaluate residuals

```{r}

par(mfrow = c(1,2))
hist(res_arima$residuals)
qqnorm(res_arima$residuals)

```

```{r}

forecast_res <- forecast(res_arima, h = 60)
plot(forecast_res)

#if I want to conver the information to adata frame (eg. for ggplotting), then I can do that by : 

res_df <- data.frame(forecast_res)


```

