---
title: "244_Assignment_1_COLON"
author: "Mario Colon"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Import Data 

```{r packages_data}

library(tidyverse)
library(nnet)
library(leaflet)
library(readr)
BluesStyle <- read_csv("Downloads/244/Assignment_1/BluesStyle.csv")
View(BluesStyle)

```

#Task 3

Explore Data

```{r data_fun}

BluesStyle$ThumbStyle <- as.factor(BluesStyle$ThumbStyle)
BluesStyle$Region <- as.factor(BluesStyle$Region)

BsMLR <- multinom(ThumbStyle ~ Region + BirthYear, data = BluesStyle)

Frame <- data.frame(Region = rep(c("Texas", "Delta", "East"), each = 69), BirthYear = rep(seq(1873, 1941), 3))

PredProb <- data.frame(Frame, predict(BsMLR, newdata = Frame, type = "probs"))

prob_gather <- PredProb %>% 
  gather(Preference, Probability, Alternating:Utility)

ggplot(prob_gather, aes(x=BirthYear, y=Probability)) +
  geom_line(aes(color=Preference)) +
  facet_wrap(~Region) +
  xlab("Birth Year") +
  ggtitle("Blues Style by Birth Year and Region\n(1874 - 1940)") +
  theme_bw()
  

```

Figure 1. Probability of blues guitarists using the alternative-, utility- or dead-thumb style taking into account geography (Region) and Birth Year.

Following a multinomial logistic regression, we see general trends in the probability of blues guitar thumb style differing along regional and birth year lines. In the Delta, a low probability of Alternating- style is persistent while a shift from Dead- to Utility-thumb style occurs as the year of guitarist birth moves from 1870 to 1941. The same shift from Dead- to Utility-thumb style occurs in the East, however the overall probability remains low (<40%) while the Alternative-thumb style remains at high probability persistence above 50% from 1870 to 1941. Lastly, in Texas a plummet of the lielihood guitarists will use th Dead-thumb style in 1870 from almost 95% to just above 50% in 1941 is seen, with a slow uptick of the Utility-thumb style from close to 5% to about 40% and the Alternative-style accounting for the last 10% in 1941.


#Task 4

```{r taco_review}

Los_Agaves <- rep(c(1,2,3,4,5), times = c(30,22,30,109,326))
Lillys_Tacos <- rep(c(1,2,3,4,5), times = c(6,13,19,83,199))

hist(Los_Agaves)
hist(Lillys_Tacos)

taco_review <- wilcox.test(Los_Agaves,Lillys_Tacos)
taco_review

```

Following the performance of a Mann-Whitney-U Test (W= 81768, p = 0.75), we retain the null hypothesis that the median Yelp reviews for Los Agaves (n = 517) and Lilly's Tacos (n = 320) do not significantly differ (i.e., there is not sufficient evidence to make us think that average Yelp Reviews for the two taco shops do differ significantly).


