---
title: "Assignment_2"
author: "Mario Colon"
date: "February 24, 2018"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#Load Packages

```{r, results='hide', message=FALSE}

library(tidyverse)
library(Ecdat)
library(plm)
library(lmtest)
library(quantreg)
library(car)
library(boot)
library(nlstools)

```



#Task 3

Fish stuff

```{r, results='hide', message=FALSE}

fish  <- read_csv("fish_catch.csv")

fish_fun <- fish %>% 
  select(Wild_Catch, Farmed_Fish, Total_Fish_Produced, Year1)

fish_fun

ggplot(fish_fun, aes(x = Year1, y = Wild_Catch)) +
  geom_point()

r_est <- lm(log(fish_fun$Wild_Catch[1:7]) ~ fish_fun$Year1[1:7])
r_est

#Ct = A / (1 + Be^-rt)

#Estimate for K ~ 88
#Estimate for C0 ~ 17.2
#Estimate for B (K-C0)/C0 = 4.2

#Estimate for A ~ 88
#Estimate for B ~ 4.2
#Estimate for r ~ .06407

fish_fit <- nls(Wild_Catch ~ A / (1 + B*exp(-r*Year1)),
                data = fish_fun,
                start = list(A = 88, B = 4.2, r = .06407),
                trace = TRUE
                )


A <- coef(fish_fit)[1]
B <- coef(fish_fit)[2]
r <- coef(fish_fit)[3]

time_seq <- seq(0, 100, length = 300)
time_seq


fish_pred <- A/(1+B*exp(-r*time_seq))
fish_pred

pred_df <- data.frame(time_seq, fish_pred)
pred_df

ggplot(fish_fun, aes(x=Year1, y=Wild_Catch)) +
  geom_point(color = "blue", size = 3) +
  theme_bw() +
  geom_line(data = pred_df, aes(x = time_seq, y = fish_pred), color = "red") +
  xlab("Time (years)") +
  ylab("Wild Catch (million tons)") +
  ggtitle("Prediction of Wild Fish Catch Per Year")



```

**Figure 1. Prediction of Wild Fish Catch** Wild fish caught per year has increased logistically over time (Time adjusted; 1950 = 0). Despite more fish caught, the rate of capture has decreased over time, with a carrying capacity of 100 million tons of wild fish caught per year possible in the near future. 

*Final Equation: Wild Fish Catch = 88 / (1 + 4.2e^-.06407t)*


#Task 4

In the study, 22 of 36 surveyed UCSB community members (61%) identifying as genderqueer responded that they had personally experienced “exclusionary, offensive, hostile or intimidating conduct” (compared to 26% and 19% for those identifying as women and men, respectively).

Create a vector reflecting the collected survey data, then find the bootstrapped 95% confidence interval for the proportion of genderqueer individuals experiencing exclusionary conduct based on the 2014 UCSB survey data.

```{r}

#n=35
#nq = 22 = 61%

n=36
exclusion <- sample(1, n, TRUE)
exclusion[sample(1:36, .39 * n, FALSE)] <- 0
table(exclusion)

mean_exclusion <- function(x,i) {mean (x[i])}

bootex_10000 <- boot(exclusion, mean_exclusion, R = 10000)
hist(bootex_10000$t)

bootex_graph <- data.frame(bootex_10000$t)

ggplot(bootex_graph, aes(bootex_10000$t)) +
  geom_histogram(binwidth = .03, fill = "darkgreen", colour = "black") +
  xlab("Proportion") +
  ylab ("Frequency") +
  ggtitle ("Genderqueer Individuals Experiencing Hostility") +
  theme_bw() 

ex_ci <- boot.ci(bootex_10000, conf = .95, type = "perc")
ex_ci 

```
**Figure 2. Genderqueer individuals experiencing hostility** Results of bootstraped data (CI = 95%) from survey exploring the proportions of individuals who identify as genderqueer (61%) who experienced "exclusionary, offensive, hostile or intimidating conduct" (n = 36) at UCSB. Source: 2014 UCSB Campus Climate Project Final Report (prepared by Rankin & Associates Consulting

#Task 5

###[d]

```{r load, results='hide', message=FALSE}

library(tidyverse)

```
###[e]

```{r, results='hide', message=FALSE}

ca_pest <- read_csv("ca_pest.csv")
ca_pop <- read_csv("ca_pop.csv")

```

###[f - i]

```{r}

ca_merge <- full_join(ca_pest, ca_pop) %>% 
  mutate(PesticidePounds_SqMile = PestPounds/CountyArea) %>% 
  mutate(Population1 = Population/1000) %>% 
  mutate(MedFamilyIncome1 = MedFamilyIncome/1000) %>% 
  arrange(desc(PesticidePounds_SqMile)) %>% 
  select(County, PesticidePounds_SqMile, Population1, MedFamilyIncome1)

ca_merge

```


##[j]
```{r, results='hide', message=FALSE}

ggplot(ca_merge, aes(x = MedFamilyIncome1, y = PesticidePounds_SqMile, size = Population1)) +
        geom_point(colour = "purple", alpha = .8) +
  labs(size = "Population Size \n(thousands)") +
  ylab("Pesticide Load (1000 lbs/square miles)") +
  xlab("Annual Medium Family Income (thousands)") +
  ggtitle("Pesticide Concentration by County") +
  annotate("text", x = 68, y = 8700, label = "San Joaquin", size = 4) +
  geom_smooth(method = lm, se = FALSE, show.legend = FALSE) +
  theme_bw()

```

**Figure 3. Pesticide Concentration by County** Pesticide concentrations per county decreases as medium famiy income increase. Outlier of San Joaquin County exists, witha  pesticide use of 8,645,000 lbs/square mile a medium family income of $59,600 per year Source: Pesticide data: 2014 CA pesticide application (by county) from the California Department of Pesticide Regulation & California population & income data: U.S. Census Bureau. American Community Survey, 2010- 2014 American Community Survey 5-Year Estimates