---
title: "Colon_Lab2"
author: Mario Colon
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

#a. Load Packages - Binary Logistic Regression 

```{r packages, include = FALSE}

library(tidyverse)
library(nnet)
library(leaflet)
library(readr)

```

Ger our Badwater Ultramarathos 2013 data

```{r load_data}

badwater_13 <- read_csv("/Users/brianthomas/Downloads/244/Lab_2/badwater_13.csv")
View(badwater_13)

```

#b. Reassigning 'finish' and 'sex' as factos 

```{r make_factors}

badwater_13$finish <- as.factor(badwater_13$finish)
badwater_13$sex <- as.factor(badwater_13$sex)

contrasts(badwater_13$sex) #give you what R has assigned to zeros and ones

```

#c. Run the binary logistic regression model 

```{r bw_model}

bw_model <- glm(finish ~ sex + age, data = badwater_13, family = "binomial") #generalized linear model

bw_model #summary of equation 

```

#e. Make predictions for the model in terms of actual probabilities 

Make some data that I will use to make predictions with: 

```{r model_data}

age_vector <- rep(seq(from = 25, to = 75), 2)
sex_vector <- c(rep("m",51), rep("f", 51))

new_data <- data_frame(age_vector, sex_vector)
colnames(new_data) <- c("age", "sex")

```

Make some predictions using predict() function

```{r predictions}

prediction <- predict(bw_model, newdata = new_data, type = "response", se.fit = TRUE)

graph_data <- data.frame(new_data, prediction$fit, prediction$se.fit)
graph_data

colnames(graph_data) <- c("age", "sex", "probability", "se")

```

#g. Graph the probabilities of finishing Badwater

```{r graph_badwater}

ggplot(graph_data, aes(x=age, y=probability)) + 
  geom_line(aes(color=sex)) + 
  geom_ribbon(aes(ymin=probability-se, ymax=probability+se, fill = sex), alpha = 0.3)

```

##2. Multiple Logistic Model 

```{r import_data}

purchase <- read_csv("Downloads/244/Lab_2/purchase.csv")
View(purchase)


```

a.Update to factors 

```{r factor_change}

purchase$Buy <- as.factor(purchase$Buy)
purchase$EdLevel <- as.factor(purchase$EdLevel)

purchase$EdLevel <- relevel(purchase$EdLevel, ref = "HS")

```

b. MLR

```{r mlr}

PurchaseMLR <- multinom(Buy ~ EdLevel + Income, data = purchase)

```

c. Make some new data that we'll have the model make predictions for

```{r mlr_predictions}

Frame <- data.frame(EdLevel = rep(c("HS", "College", "Graduate"), each = 121), Income = rep(seq(0, 120), 3))

```

d. Make prediction using the model

```{r make_predictions}

PredProb <- data.frame(Frame, predict(PurchaseMLR, newdata = Frame, type = "probs"))

```

gather {} -- similar to melt

```{r gather}

prob_gather <- PredProb %>% 
  gather(Choice, Probability, Generic:Organic) #create a new column called choice and predicted

```

Graph it!

```{r}

ggplot(prob_gather, aes(x=Income, y=Probability)) +
  geom_line(aes(color=Choice)) +
  facet_wrap(~EdLevel)

```

##3 Intro to leaflet

```{r leaflet_intro}

mymap <- leaflet() %>% 
  addTiles() %>% 
  addMarkers(lng=-119.6982, lat = 34.4208, popup = "Zooming Maps")
mymap



```

