---
title: "Lab_7_Variograms & Kriging"
author: "Mario Colon"
date: "March 1, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


1. Packages

```{r}

library(tidyverse)
library(sf)
library(sp)
library(gstat)
library(rgdal)
library(tmap)

```

2. Get Data

```{r}

lat_lon <- read_csv("lat_lon.csv")
fire_pm25 <- read_csv("fire_pm25.csv")
counties <- st_read(dsn = ".", layer = "california_county_shape_file")

```

3. Combine PM2.5 attribute date with the latitude/longitude information 

```{r}

df <- full_join(lat_lon, fire_pm25) 

df <- df %>% 
  filter(name != "NA")

```

4. Convert to simple features spatial data, and we're going to set the CRS

```{r}

df_sf <- st_as_sf(df, coords = c("latitude", "longitude")) #creates a new "geometry" column which merges the lat/long into one

st_crs(df_sf) <- 4326 #standard reference for map projection (1984)

st_crs(counties) <- 4326 #double check counties are projected to same map 

 
```

5. Filter the data to only retain air quality observations from 12/10/17

```{r}

pm_12_10 <- df_sf %>% 
  filter(summary_date == "12/10/17") %>% 
  select(pm25_davg)
```

6. Make a point plot using ggplot with geom_sf

```{r}

#plot(pm_12_10)
#plot(counties)

ggplot(pm_12_10) +
  geom_sf(data = counties) +
  geom_sf(aes(color = pm25_davg))

```

7. Create a simplified data frame, set coordiantes, and CRS

```{r}

df2 <- df %>% 
  filter(summary_date == "12/10/17") %>% 
  select(longitude, latitude, pm25_davg) 

coordinates(df2) <- ~ latitude + longitude
proj4string(df2) <- CRS("+init=epsg:4326")

bubble(df2, "pm25_davg")

```

8. Create a variogram, and fit a variogram model

```{r}


pm_vg <- variogram(pm25_davg ~ 1, df2)

plot(pm_vg)

#nugget: 100
#range: 300
#sill: 450

vg_fit <- fit.variogram(pm_vg, vgm(c("Exp", "Sph", "Gau")))
plot(pm_vg, vg_fit)

```
9. New grid of pixels is over which we want to interpolate 

```{r}

Long <- seq(-125, -114, length = 100)
Lat <- seq(32, 42, length = 100)

Grid <- expand.grid(Long, Lat)

colnames(Grid) <- c("Long", "Lat")

coordinates(Grid) <- ~ Long + Lat
gridded(Grid) = TRUE
proj4string(Grid) <- CRS("+init=epsg:4326")

plot(Grid)

```

10. Kriging

```{r}

pm_krige <- krige(pm25_davg ~1, df2, newdata = Grid, model = vg_fit)


```

11. Visualize the results

```{r}

krige_df <- data.frame(Grid$Long, Grid$Lat, pm_krige$var1.pred)
colnames(krige_df) <- c("Long", "Lat", "Predicted")

krige_gg <- ggplot() + 
  geom_tile(data = krige_df, aes(x = Long, y = Lat, fill = Predicted)) +
  geom_sf(data = counties, fill = "NA", color = "white")

krige_gg

```

