---
title: "Lab 1"
author: "Mario Colon"
date: "1_18_18"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Lab Objectives 

- Markdown regresher 
- Data wrangling refresher (tidyverse)
- Pipe operator (%>%)
- Recap data visualization with ggplot
- Little baby intro to Shiny apps 

#Part 1: Load Packages 

```{r load_packages}

library(tidyverse) #load tidyverse package
library(readr)

```

##Part 2: Load Data 

```{r data_upload}

hp_aggression <- read_csv("/Users/brianthomas/Downloads/244/Lab_1/hp_aggression.csv")

```

##Part 3: Data wrangling and pipe operator practice 

- select(): Select specified columns from a df
- filter(): Select rows by setting conditions to match
- mutate(): Adds columns based on calculators for existing
- arrange(): Sorting variables 
- group_by(): Assign grouping to variable entires, and can perform operations by group 

```{r data_wrangling}

hp_df1 <- hp_aggression %>% #pipe allows you to perform multiple functions (nested)
  select(Name, aggressions, mentions) %>% 
  mutate(rate = aggressions/mentions) %>% #acts of aggression divided by total mentions in books
  group_by (Name) %>% #groups 'Names' and associated fields
  mutate(average_rate = mean(rate)) %>% #average rate of agression BY 'Name'
  ungroup() %>% #take out background information that groups 'Names' in this example
  select(Name, average_rate)  %>% #ONLY select names and average rates of aggression
  distinct(Name, average_rate)  %>% #restrict to ONLY 'Name' and 'Average Rate'
  arrange(-average_rate) %>% 
  head(10)

```

##Part 4. ggplot Refresher

1. Tell R that you want to use ggplot
2. Tell it what data you want to use (including what x/y are)
3. Tell it what type of graphic you want to create

```{r set_levels}

hp_df1$Name <- factor(hp_df1$Name, levels = hp_df1$Name[order(hp_df1$average_rate)]) #set order of 'Names' to the order of 'average rate' as in highest to lowest rather than alphabetical order (default)

```

Make the graph!

```{r hp_graph}

ggplot(data = hp_df1, aes(x = Name, y =  average_rate)) +
  geom_bar(stat = "identity", aes(fill = Name)) +
  coord_flip() 

```




