---
title: "Lab Week 5 - Missing Data Exploration and Multiple Imputation"
author: "Mario Colon"
date: "February 15, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

##Step 1. 

Load Packages (tidyverse, VIM, mice)

```{r packages}

library(tidyverse)
library(VIM)
library(mice)

```

##Step 2.

Read in the data (df_missings.csv)

```{r load_in_data}

df <- read_csv("df_missings.csv")

```

##Step 3. 

a. Identify complete cases and missing cases (using VIM package, which helps visualize missingness)

```{r complete_cases}

cc <- df[complete.cases(df),]
missings <- df[!complete.cases(df),] #! asks for NON complete.cases

```

b. Visually identify the structure of missingness 

```{r missingness}

aggr(df, prop = F, number = T) #left, number of overall missing values. right, total cases of missing specific variables 
 
```

c. Another way .... *matrixplot*

```{r matrix}

#quartz()
matrixplot(df[1:3]) #only use the first 3 columns

```

##Step 4. 

Multiple imputations (mice package & function), and explore the complete cases 

```{r}

df$sex <- as.factor(df$sex)
df$smoker <- as.factor(df$smoker)
class(df$sex)#check factors to make sure they are factors

imputed <- mice(df, m = 5)
#summary(imputed)

imputed$imp$age

complete(imputed, action = 4)

```

##Step 5. 

Perform regreassion on each of the complete cases seperately using the with() function, and then pool the results using the pool() function

```{r}

lm_cc <- with(imputed, lm(sbp~weight))
lm_cc

impute_pooled <- pool(lm_cc)
impute_pooled  
```

