---
title: "Assignment2_Task5"
author: "Mario Colon"
date: "February 26, 2018"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

###d. Load the tidyverse

```{r load, results='hide', message=FALSE}

library(tidyverse)

```
###e. Load the two datasets

```{r, results='hide', message=FALSE}

ca_pest <- read_csv("ca_pest.csv")
ca_pop <- read_csv("ca_pop.csv")
ca_pest
ca_pop

```

###f. Merge the two data frames by matching character strings in the County columns
###g. Create a new column for pesticide applied (pounds) per square mile
##h. Sort the new data frame from highest to lowest by the pesticide (pounds) per square mile column you created in (g)
##i. Keep only the columns for: county name, pesticide applied per square mile, median family income and population

```{r}

ca_merge <- full_join(ca_pest, ca_pop) %>% 
  mutate(PesticidePounds_SqMile = PestPounds/CountyArea) %>% 
  arrange(desc(PesticidePounds_SqMile)) %>% 
  select(County, PesticidePounds_SqMile, Population, MedFamilyIncome)

```


##j. Create a finalized bubble plot of median household income versus pesticide application per square mile, with the size of the ‘bubbles’ based on county population. Add a visual line of best fit (use geom_smooth, without an error ribbon – you do not need to actually find the model equation for this assignment). Add a label (county name) to the notable outlier on the graph. Include a figure caption.

```{r}

pest_income <- ggplot(ca_merge, aes(x = MedFamilyIncome, y = PesticidePounds_SqMile, size = Population)) +
        geom_point() +
  geom_smooth(se = FALSE, show.legend = FALSE)

pest_income

```

