---
title: "Lab_4"
author: "Mario Colon"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

1. Load Packages

```{r load_packages, include = FALSE}

library(tidyverse)
library(Ecdat)
library(plm)
library(lmtest)
library(quantreg)
library(car)

```

Q: What is the effect of the average price of cigarette on purchases. 

2. Simplify the dataset to only retain variables "state", "year", "packpc", "avgprs"

```{r}

cigs_panel <- Cigarette %>% 
  select(state, year, packpc, avgprs)

```

3. Fixed effects model (within state)

```{r}

cigs_model <- plm(packpc ~ avgprs, 
                  data = cigs_panel,
                  index = c("state","year"),
                  model = "within")

cigs_model
#summary(cigs_model) #...but we want to use the robus standard error in case of heteroscedasticity

coeftest(cigs_model, vcov. = vcovHC(cigs_model, type = "HC1"))

```

Model coefficient say --> A negative relationship between average price and packs sold per capita

N0 = There is no significant relationship betweeen average cigarette pack price and packs sold per capita

4. Fixed Effects Model fo time and entity

```{r}

et_cigs_model <- plm(packpc ~ avgprs, 
                     data=cigs_panel,
                     index = c("state", "year"),
                     model = "within",
                     effect = "twoways") #effect = takes into account time-fixed effect variable entities into the model 
et_cigs_model

coeftest(et_cigs_model, vcov = vcovHC(et_cigs_model, type = "HC1"))

```

5. So which of these should I pick? Entity fixed effects or Entity/Time FE?

```{r}

pFtest(et_cigs_model, cigs_model) #Just as well of ONLY including entity fixed effect
  

#Test the hypothesis that there is no significant benefit to including the TIMED FIXED EFFECT (null). Reject NULL, which accepts the alternative hypothesis that there is a benefit to include the TIMED FIXED EFFECTS 
```

6. Least Squares Dummy Variable Regression (for the states with the top 5 populations as of 1995)

```{r}

cigs_panel2 <- Cigarette %>% 
  select(state,year,packpc,avgprs) %>% 
  filter(state == "CA" | state == "TX"| state == "NY" | state == "FL" |state == "PA")

```

Least Squares Dummy Variable Regression (state FE)

```{r}

lsdv_cigs <- lm(packpc ~ avgprs + state, data = cigs_panel2)

lsdv_cigs

```

```{r}

cigs_panel_plot <- cigs_panel2 %>% 
  droplevels()

levels(cigs_panel_plot$state)


```

```{r fig.height=6, fig.width=6}

scatterplot(cigs_panel_plot$packpc ~ cigs_panel_plot$avgprs | cigs_panel_plot$state,
            xlab = "Average Price",
            ylab = "Packs per Capita",
            smooth = FALSE,
            legend.title = "State")

```

